RELATION BETWEEN STAR FORMATION RATE, GAS MASS AND STELLAR MASS IN THE ANDROMEDA GALAXY

### 2015-03-24 draft3.tex
from untitled

\begin{equation}
\label{equ:es_org}
\eqsigmasfr \propto \eqsigmagas^{\eqnprime} \eqsigmastar^{\beta}
\end{equation}
where \sigmasfr is SFR surface density, \sigmagas and \sigmastar are the gas mass and the stellar mass surface densities. \nprime and $\beta$ are the power law indexes. \cite{Shi11} calculated power indexes are $\eqnprime = 1.13 \pm 0.05$ and $\beta = 0.36\pm0.04$ in a global case. By testing this relation on sub-kiloparces resolution regions on 12 spiral galaxies, they showed that the extended Schmidt law predicts SFR as well as the K-S law for spatially resolved regions ($\sim$1 kpc sizes). They demonstrated the power indexes for the local regions are $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$. They concluded that this law is acceptable for low surface brightness galaxies and regions where the KS law fails.

@@

Furthermore, the range of the power index of K-S law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10,Ford13}. %Different groups, using different SFR or gas mass tracers, applied the K-S law on the M31 and have very different power indexes. 
In the most recent work of the K-S law in M31, \cite{Ford13}, test this law on six regions from the centre of the galaxy using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus HI maps, and total gas calculated from dust emission). The power indexes they measure for each map and each region vary between 0.6 to 2.03. The origin of these contrary results is still ongoing question. It is not obvious what makes these differences in the power law indexes calculated by different groups. Whether it depends to distance from galaxy, metallicity, gas tracers, SFR tracers, fitting methods, or this is because of the K-S law does not work on the M31 at all. If we assume the last case is valid, testing extended Schmidt law on the Andromeda galaxy would help to solve the problem with these controversial results.

@@

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fir_vs_h2.png}
        \caption{SFR,TIR vs surface density of H$_2$}
        \label{fig:es,all,fir,h2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fir_vs_hi.png}
        \caption{SFR,TIR vs surface density of HI}
        \label{fig:es,all,fir,hi}
    \end{subfigure}
    \hfill
   \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fir_vs_tot.png}
        \caption{SFR,TIR vs surface density of total gas}
        \label{fig:es,all,fir,tot}
    \end{subfigure}
    \hfill
     \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fuv_vs_h2.png}
        \caption{SFR,FUV+24\um vs surface density of H$_2$}
        \label{fig:es,all,fuv,h2}
    \end{subfigure}
     \hfill
   \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fuv_vs_hi.png}
        \caption{SFR,FUV+24\um vs surface density of HI}
        \label{fig:es,all,fuv,hi}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fuv_vs_tot.png}
        \caption{SFR,FUV+24\um vs surface density of total gas}
        \label{fig:es,all,fuv,tot}
    \end{subfigure}
    \caption{The result from fitting the extended Schmidt law on data from whole galaxy using pixel by pixel method. The plots show the SFR vs surface density of gas, and z-axis is the surface density of the stellar mass. Each figure shows different combinations of the SFR tracer and gas mass tracer results. Plots have a different pixel size. Each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents regions $\sim$30~Kpc and points in plots with surface density of HI or total gas mass, represents region in $\sim$155~Kpc.}
    \label{fig:es,all}
\end{figure*}

@@

Our results for the global case of the K-S law show that using total gas gives a sub-linear relation between the surface density of the SFR and the total gas surface density. While, for using the H$_{2}$ only gas or HI only gas we find the super-linear relation. These results are different from power indexes estimated by \cite{Ford13}, $N=2.03\pm0.04$ in case of total gas and $N=0.6\pm0.01$ in case of H$_{2}$ only gas. \cite{Tabatabaei10} estimated the K-S law power index $N=1.30\pm0.05$ using the total gas and $N=0.96\pm0.03$ using the H$_{2}$ only gas. The reason behind these differences is mostly because of the statical method we chose.The OLS fitting on the H$_{2}$ only gas gives us the power index of $N=0.54\pm0.003$ which is in good agreement with previous results.
%PB: well, 0.54 agrees with 0.6, but it doesn't agree with 0.96. If your
%uncertainties and theirs are right, 0.54 pm 0.003  is actually in poor agreement 
% with 0.06 pm 0.01- it's at least 6 standard deviations away.
% so need to clarify your argument here.

 \cite{Bigiel08} argued that there is no universal relationship between the surface density of the total gas and the SFR. They also showed that the SFR and the molecular hydrogen have a linear relationship. Furthermore, \cite{Shetty13} used the same data as \cite{Bigiel08} and argued that using the hierarchical Bayesian fit leads to significant galaxy-by-galaxy variation between power indexes and all of them are lower than \cite{Bigiel08}.

@@

 The fitting results on the regions with different distances from the centre of the galaxy are more similar to the results from \cite{Shi11}. Taking the average of our three regions leads us to the conclusion that using molecular gas only or atomic gas only $\beta$ is 0.60 and 0.55 which is very close to prediction of \cite{Shi11}. In the local case, the same as global case power indexes calculated using total gas surface density, are much smaller than the original suggestion of \cite{Shi11}. 
% PB: can you explain why this might be?

>>>>

\begin{equation}
\label{equ:es_org}
\eqsigmasfr \propto \eqsigmagas^{\eqnprime} \eqsigmastar^{\beta}
\end{equation}
where \sigmasfr is SFR surface density, \sigmagas and \sigmastar are the gas mass and the stellar mass surface densities. \nprime and $\beta$ are the power law indices. \cite{Shi11} calculated power indices are $\eqnprime = 1.13 \pm 0.05$ and $\beta = 0.36\pm0.04$ in a global case. By testing this relation on sub-kiloparces resolution regions on 12 spiral galaxies, they showed that the extended Schmidt law predicts SFR as well as the K-S law for spatially resolved regions ($\sim$1 kpc sizes). They demonstrated the power indices for the local regions are $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$. They concluded that this law is acceptable for low surface brightness galaxies and regions where the KS law fails.

@@

Furthermore, the range of the power index of K-S law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10,Ford13}. %Different groups, using different SFR or gas mass tracers, applied the K-S law on the M31 and have very different power indices. 
In the most recent work of the K-S law in M31, \cite{Ford13}, test this law on six regions from the centre of the galaxy using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus HI maps, and total gas calculated from dust emission). The power indices they measure for each map and each region vary between 0.6 to 2.03. The origin of these contrary results is still ongoing question. It is not obvious what makes these differences in the power law indices calculated by different groups. Whether it depends to distance from galaxy, metallicity, gas tracers, SFR tracers, fitting methods, or this is because of the K-S law does not work on the M31 at all. If we assume the last case is valid, testing extended Schmidt law on the Andromeda galaxy would help to solve the problem with these controversial results.

@@

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fir_h2_f.png}
        \caption{SFR,TIR vs surface density of H$_2$}
        \label{fig:es,all,fir,h2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fir_hi_f.png}
        \caption{SFR,TIR vs surface density of HI}
        \label{fig:es,all,fir,hi}
    \end{subfigure}
    \hfill
   \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fir_tot_gas_f.png}
        \caption{SFR,TIR vs surface density of total gas}
        \label{fig:es,all,fir,tot}
    \end{subfigure}
    \hfill
     \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fuv_h2_f.png}
        \caption{SFR,FUV+24\um vs surface density of H$_2$}
        \label{fig:es,all,fuv,h2}
    \end{subfigure}
     \hfill
   \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fuv_hi_f.png}
        \caption{SFR,FUV+24\um vs surface density of HI}
        \label{fig:es,all,fuv,hi}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{es_tot_fuv_tot_gas_f.png}
        \caption{SFR,FUV+24\um vs surface density of total gas}
        \label{fig:es,all,fuv,tot}
    \end{subfigure}
    \caption{The result from fitting the extended Schmidt law on data from whole galaxy using pixel by pixel method. The plots show the SFR vs surface density of gas, and z-axis is the surface density of the stellar mass. Each figure shows different combinations of the SFR tracer and gas mass tracer results. Plots have a different pixel size. Each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents regions $\sim$30~Kpc and points in plots with surface density of HI or total gas mass, represents region in $\sim$155~Kpc.}
    \label{fig:es,all}
\end{figure*}

@@

Our results for the global case of the K-S law show that using total gas gives a sub-linear relation between the surface density of the SFR and the total gas surface density. While, for using the H$_{2}$ only gas or HI only gas we find the super-linear relation. These results are different from power indices estimated by \cite{Ford13}, $N=2.03\pm0.04$ in case of total gas and $N=0.6\pm0.01$ in case of H$_{2}$ only gas. \cite{Tabatabaei10} estimated the K-S law power index $N=1.30\pm0.05$ using the total gas and $N=0.96\pm0.03$ using the H$_{2}$ only gas. The reason behind these differences is mostly because of the statical method we chose.The OLS fitting on the H$_{2}$ only gas gives us the power index of $N=0.54\pm0.003$ which is in good agreement with previous results.
%PB: well, 0.54 agrees with 0.6, but it doesn't agree with 0.96. If your
%uncertainties and theirs are right, 0.54 pm 0.003  is actually in poor agreement 
% with 0.06 pm 0.01- it's at least 6 standard deviations away.
% so need to clarify your argument here.

 \cite{Bigiel08} argued that there is no universal relationship between the surface density of the total gas and the SFR. They also showed that the SFR and the molecular hydrogen have a linear relationship. Furthermore, \cite{Shetty13} used the same data as \cite{Bigiel08} and argued that using the hierarchical Bayesian fit leads to significant galaxy-by-galaxy variation between power indices and all of them are lower than \cite{Bigiel08}.

@@

 The fitting results on the regions with different distances from the centre of the galaxy are more similar to the results from \cite{Shi11}. Taking the average of our three regions leads us to the conclusion that using molecular gas only or atomic gas only $\beta$ is 0.60 and 0.55 which is very close to prediction of \cite{Shi11}. In the local case, the same as global case power indices calculated using total gas surface density, are much smaller than the original suggestion of \cite{Shi11}. 
% PB: can you explain why this might be?
